Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-28 manuscript.Rmd
Add Alex's edits pt. 2

### Syria as Source and Target
By adding Syria as a source in the data filtering, the event dataset increased in size by `r num_source_target-num_target` samples. These additional observations are times where Syria initiated
an event with another country. Events initiated by Syria but directed internally
within the country were already captured by the target-only filtering. Taking outwardly directed events into account dramatically changed the coupling between all events and social cohesion. There is no longer a significant number of shared trajectories or line lengths, indicating that the cohesion on Twitter is not tied to the frequency of overall daily events. Since source events are at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them; considering additional source events then overshadowed the relationship between target events and social cohesion online. In contrast, there was a slight increase in coupling strength between positive events and social cohesion that once again can only be due to the externally directed events. These two time series showed greater stability in their coupling (reflected in L). However, the significant ENTR metric suggests that there is more variability in the coupling, so rather than interpreting these two changes as a fundamental change in coupling between source events and positive events, we interpret this as a breaking-up of the trajectories formed by the target events. Although the coupling between social cohesion with negative events were largely unchanged, there was a slight decrease in coupling strength (reflected in maxL) and an increase in complexity of shared trajectories (reflected in rENTR). Similarly to that of positive events, this change may not be reflective of source events themselves, but rather a disruption of the relationship with target events.

@@

Nonlinear methods have been transformative for a variety of research areas
[including psychology, @coco2014cross]. One of the goals of the present work was
to introduce variants of one kind of nonlinear method---specifically, recurrence
quantification analysis---to this research area. While a number of excellent
guides can provide detailed explanations of the methods and their statistical
underpinnings [e.g., @riley2005tutorials; @webber1994dynamical;
@webber2005recurrence], one of the most important considerations that should be
briefly summarized here is about data.

@@

This methodology should be of great interest to social scientists investigating
social mobilization. It has potential applications for gender studies and
the #MeToo movement and for the relationship between social protest and repression
during the Black Lives Matter protests. This methodological
approach can help us better understand the fundamental human social mechanisms underlying
social media and its influence on human behavior in real life. Given that many
governments enact repressive measures when they determine that collective action
by citizens is imminent, this methodology should help to improve the predictive
power of using social media data in estimating repressive behavior. If social
media messages are increasing in cohesion, this may represent a threat to civil
and political liberties of citizens engaging in collective action.

>>>>

### Syria as Source and Target
By adding Syria as a source in the data filtering, the event dataset increased in size by `r num_source_target-num_target` samples. These additional observations are times where Syria initiated
an event with another country. Events initiated by Syria but directed internally
within the country were already captured by the target-only filtering. Taking outwardly directed events into account dramatically changed the coupling between all events and social cohesion. There is no longer a significant number of shared trajectories or line lengths, indicating that the cohesion on Twitter is not tied to the frequency of overall daily events. Since source events are at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them; considering additional source events then overshadowed the relationship between target events and social cohesion online. In contrast, there was a slight increase in coupling strength between positive events and social cohesion that once again can only be due to the externally directed events. These two time series showed greater stability in their coupling (reflected in L). However, the significant ENTR metric suggests that there is more variability in the coupling, so rather than interpreting these two changes as a fundamental change in coupling between source events and positive events, we interpret this as a breaking-up of the trajectories formed by the target events. Although the coupling between social cohesion with negative events were largely unchanged, there was a slight decrease in coupling strength (reflected in maxL) and an increase in complexity of shared trajectories (reflected in rENTR). Similarly to that of positive events, this change may not be reflective of source events themselves but rather a disruption of the relationship with target events.

@@

Nonlinear methods have been transformative for a variety of research areas
[including psychology; @coco2014cross]. One of the goals of the present work was
to introduce variants of one kind of nonlinear method---specifically, recurrence
quantification analysis---to this research area. While a number of excellent
guides can provide detailed explanations of the methods and their statistical
underpinnings [e.g., @riley2005tutorials; @webber1994dynamical;
@webber2005recurrence], one of the most important considerations that should be
briefly summarized here is about data.

@@

This methodology should be of great interest to interdisciplinary scientists investigating
social mobilization. It has potential applications for gender studies and
the #MeToo movement and for the relationship between social protest and repression
during the Black Lives Matter protests. This methodological
approach can help us better understand the fundamental human social mechanisms underlying
social media and its influence on human behavior in real life. Given that many
governments enact repressive measures when they determine that collective action
by citizens is imminent, this methodology should help to improve the predictive
power of using social media data in estimating repressive behavior. If social
media messages are increasing in cohesion, this may represent a threat to civil
and political liberties of citizens engaging in collective action.
